---
title: "eds221-day8-task"
format: html
editor: visual
---

```{r}
# General use packages:
library(tidyverse)
library(here)
library(janitor)

# Specifically for plots:
library(patchwork)
library(ggrepel)
library(gghighlight)
library(paletteer)
#library(ggExtra)
#library(ggbeeswarm)

# And for another dataset we'll explore:
library(gapminder)

# Spatial
library(sf)
```


```{r}
space_launch <- read_csv(here::here("data", "space_launches.csv"))
```


```{r}
space_new <- space_launch %>% 
  filter(str_detect(type, pattern = "Falcon"))



ggplot(data = space_new, aes(x = launch_year, y = type, size = 5)) + 
  geom_line() +
  labs(x = "the time of year(in respect to year)", y = "the vessel of travel(aka what spaceship it was)", title = "scottish wannabe") +
  theme_minimal() +
  theme(panel.background = element_rect(color = "lightblue", size = 5, fill = "red"), 
        plot.background = element_rect(fill = "lightblue"),
        panel.grid = element_line(color = "white", size = 7), 
        axis.text.x = element_text(color = "red"),
        axis.text.y = element_text(color = "red"))

```



    Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by sector_general

    Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by year and commodity type

    Create a subset of the data that only contains observations from 2005 on, only for observations where Sector_Detail2 contains the pattern “PG&E”, then limit to columns Calendar_Year, Sector_Detail2 and Emissions_mtCO2e.

```{r}
sf_emission <- read_csv(here::here("data", "San_Francisco_Communitywide_Greenhouse_Gas_Inventory.csv")) %>% clean_names()

sf_emission_sector_general <- sf_emission %>% 
  group_by(sector_general) %>% 
  reframe(emissions_mt_co2e)

sf_emission_year_commodity <- sf_emission %>% 
  group_by(calendar_year, commodity_type) %>% 
  reframe(emissions_mt_co2e)

sf_emission_subset <- sf_emission %>% 
  filter(calendar_year >= 2005, str_detect(sector_detail2, pattern = "PG&E")) %>% 
  reframe(calendar_year, sector_detail2, emissions_mt_co2e)
```


Create a finalized graph (as perfect as you can make it) using the San Francisco GHG emissions dataset. You get to choose what you want to visualize. You can pick which variables & observations you’re interested in. You may want to do some wrangling / summarizing first.

Once you’ve decided on what to plot, create the best graph that you can to communicate what’s going on with the data.

Once you’re done, drop your best graph (as a .png or .jpg) into the course Slack channel.

```{r}
# sf_count <- 
#   sf_emission %>% 
#   group_by(sector_general) %>% 
#   mutate(count_sector_general = n())
ggplot(data = sf_emission, aes(x = sector_general, y = emissions_mt_co2e)) + 
  geom_col(fill = "pink", color = "black") + 
  labs(x = "Sectors", y = "Emissions (mt)", title = "Amount of Emissions emitted by Sector") +
  theme_minimal() + 
  theme(panel.background = element_rect(fill = "lightgray"),
        plot.background = element_rect(fill = "lightgray"))
#look at facet to do border
ggsave
```




